---
title: "TRIO survey analyses 2018"
output: html_document 
---

```{r set_defaults, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      include = FALSE,
                      fig.width = 8)
```

```{r packages}
library(tidyverse)
library(googlesheets)
library(janitor)
library(ggmap)
library(lubridate)
library(leaflet)
library(bookdown)
library(plotly)
library(kableExtra)
library(knitr)
```

```{r functions_themes}
source("https://raw.githubusercontent.com/dgkeyes/dk-functions-and-themes/master/themes/mna_themes.R")
source("https://raw.githubusercontent.com/dgkeyes/dk-functions-and-themes/master/functions/dk_functions.R")


summarize_open_ended <- function(v) {
     responses <- post.surveys %>%
          filter(training_year == "2018" & training_type == "Online") %>%
          select(contains(v)) %>%
          set_names("response") %>%
          filter(!is.na(response)) %>%
          mutate(response = str_trim(response)) %>%
          filter(!str_detect(response, fixed("n/a", ignore_case = TRUE))) %>%
          filter(!str_detect(response, fixed("No", ignore_case = TRUE))) %>%
          filter(!str_detect(response, fixed("None", ignore_case = TRUE))) %>%
          filter(!str_detect(response, fixed("Not sure", ignore_case = TRUE)))
     
     
     
     
     responses %>%
          kable("html", col.names = "Responses") %>%
          kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
}

summarize_open_ended_pre <- function(v) {
     responses <- pre.surveys %>%
          filter(training_year == "2018" & training_type == "Online") %>%
          select(contains(v)) %>%
          set_names("response") %>%
          filter(!is.na(response)) %>%
          mutate(response = str_trim(response)) %>%
          filter(!str_detect(response, fixed("n/a", ignore_case = TRUE))) %>%
          filter(!str_detect(response, fixed("No", ignore_case = TRUE))) %>%
          filter(!str_detect(response, fixed("None", ignore_case = TRUE))) %>%
          filter(!str_detect(response, fixed("Not sure", ignore_case = TRUE)))
     
     
     
     
     responses %>%
          kable("html", col.names = "Responses") %>%
          kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
}

dk_table <- function(df, colnames) {
     df %>%
          kable("html", col.names = colnames) %>%
          kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
}

calculate_date_and_training_type <- function(dataset) {
     dataset <- dataset %>%
          mutate(training_date = mdy_hms(timestamp)) %>%
          mutate(training_month = month(training_date)) %>%
          mutate(training_year = year(training_date)) %>%
          mutate(training_type = as.character(training_month)) %>%
          mutate(training_type = str_replace(training_type, "3", "Online")) %>%
          mutate(training_type = str_replace(training_type, "4", "Online")) %>%
          mutate(training_type = str_replace(training_type, "5", "Hybrid")) %>%
          mutate(training_type = str_replace(training_type, "7", "In person")) %>%
          mutate(training_type = str_replace(training_type, "8", "In person")) %>%
          mutate(training_id = paste(training_year, training_type))
}

```


```{r get_data}

# Pre

pre.surveys.2018 <- gs_title("2018 TRIO Training Pre-Survey (Responses)")
pre.surveys.2018 <- gs_read(pre.surveys.2018) %>%
     clean_names() %>%
     mutate(if_no_how_many_other_staff_members_work_in_your_department_numerical_value_only = as.character(if_no_how_many_other_staff_members_work_in_your_department_numerical_value_only))


pre.surveys.2017.sheet <- gs_title("TRIO training data 2017 - merged")
pre.surveys.2017 <- gs_read(pre.surveys.2017.sheet, ws = "Pre") %>%
     clean_names() %>%
     mutate(if_no_how_many_other_staff_members_work_in_your_department_numerical_value_only = as.character(if_no_how_many_other_staff_members_work_in_your_department_numerical_value_only))

pre.surveys <- bind_rows(pre.surveys.2018, pre.surveys.2017)

# Post

post.surveys.2017.march <- gs_url("https://docs.google.com/spreadsheets/d/1pFKHHCSabHYB0AEsB6_Jf9Qj97gnatGGRfn2j1jW9KU/edit#gid=133904600")
post.surveys.2017.march <- gs_read(post.surveys.2017.march) %>%
     clean_names()

post.surveys.2017.may <- gs_url("https://docs.google.com/spreadsheets/d/18csE-KoqaZlKZRfmT3S26zJXmUa-gkeOwF7S9doOC3o/edit#gid=787154103")
post.surveys.2017.may <- gs_read(post.surveys.2017.may) %>%
     clean_names()

post.surveys.2017.august <- gs_url("https://docs.google.com/spreadsheets/d/13HStU4A4G1i5yG8uAIDNgWnQkMxcLL2r3FOpwJEfKXI/edit#gid=1665067623")
post.surveys.2017.august <- gs_read(post.surveys.2017.august) %>%
     clean_names()

post.surveys.2017.sheet <- gs_title("TRIO training data 2017 - merged")
post.surveys.2017 <- gs_read(post.surveys.2017.sheet, ws = "Post") %>%
     clean_names() 


post.surveys.2018 <- gs_title("2018 TRIO Training Post-Survey (Responses)")
post.surveys.2018 <- gs_read(post.surveys.2018) %>%
     clean_names()

post.surveys <- bind_rows(post.surveys.2018,
                          post.surveys.2017.march,
                          post.surveys.2017.may,
                          post.surveys.2017.august)

# Calculate months

post.surveys <- calculate_date_and_training_type(post.surveys)
pre.surveys <- calculate_date_and_training_type(pre.surveys)


```

```{r knowledge_growth}

knowledge.post <- post.surveys %>%
     select(contains("how_would_you_rate_your_current_level_of_knowledge"), training_type, training_year, training_id) %>%
     gather(key = "item", value = "rating", -training_year, -training_type, -training_id) %>%
     mutate(rating = parse_number(rating)) %>%
     mutate(item = str_replace(item, "how_would_you_rate_your_current_level_of_knowledge_about_the_following_aspects_of_the_training_you_just_completed_", "")) %>%
     mutate(item = str_replace_all(item, "_", " ")) %>%
     mutate(item = str_to_title(item)) %>%
     mutate(timing = "Post")

knowledge.pre <- pre.surveys %>%
     select(contains("currently_how_would_you_rate_your_levels_of_knowledge_and_understanding"), training_type, training_year, training_id) %>%
     gather(key = "item", value = "rating", -training_year, -training_type, -training_id) %>%
     mutate(rating = parse_number(rating)) %>%
     mutate(item = str_replace(item, "currently_how_would_you_rate_your_levels_of_knowledge_and_understanding_of_the_following_aspects_of_the_training_you_are_about_to_receive_", "")) %>%
     mutate(item = str_replace_all(item, "_", " ")) %>%
     mutate(item = str_to_title(item)) %>%
     mutate(timing = "Pre")

knowledge.growth <- bind_rows(knowledge.pre, knowledge.post) %>%
     mutate(item = str_replace(item, "Omb", "OMB")) %>%
     mutate(item = str_replace(item, "Trio", "TRIO")) %>%
     mutate(item = str_replace(item, "Asa", "As a")) %>%
     mutate(item = str_replace(item, "Difference S", "Differences")) %>%
     mutate(item = str_replace(item, "It C", "IT C")) %>%
     group_by(training_type, training_year, training_id, timing, item) %>%
     summarize(avg_rating = round(mean(rating, na.rm = TRUE), 1)) %>%
     ungroup() %>%
     # mutate(item = str_wrap(item, width = 40)) %>%
     mutate(item = str_replace(item, "Doing Budget Management Through Internal Controls And Financial Management", "Managing Budget Through Internal Controls And Financial Management")) %>%
     mutate(item = str_replace(item, "Application Of Governing Rules Of TRIO Program Components And Trio As A Whole", "Application Of Governing Rules Of TRIO Program Components And Trio As a Whole")) %>%
      mutate(item = str_replace(item, "Right And Responsibilities Of Institutions That Agree To Sponsor TRIO Grants" , "Rights And Responsibilities Of Institutions That Agree To Sponsor TRIO Grants")) %>%
     mutate(item = str_replace(item, "Difference Between Allowable And Non Allowable Costs" , "Differences Between Allowable And Non Allowable Costs")) %>%
     mutate(timing = factor(timing, levels = c("Pre", "Post"))) %>%
     mutate(popup_text = paste(timing, 
                               ": ",
                               avg_rating,
                               sep = ""))


```



# Introduction


This is a report on surveys conducted after online TRIO training in March 2018. This training was conducted by Cuyahoga Community College. More infomation available <a target="_blank" href="https://forms.tri-c.edu/PathwaysTRiOTrainingForm">here</a>. 
As of April 11, 54 (87% of those who initially registered) have successfully completed the training. 

Of the 62 participants registered for the training, 45 completed the pre survey (a 73% response rate) and 42 completed the post survey (a 68% response rate). 

Please use the arrow on the right side or the contents on the left side to navigate through the findings. 


# Institutions Represented

62 participants were involved with the March training. The locations of the institutions they represent are below. Click on any point to see the name of the institution. 


```{r geocode}

register_google(key = "AIzaSyBonrLhrEfIT08lG62TA-KOYoaoghonw4Y")

institutions.sheet <- gs_title("TRIO participants")

institutions <- gs_read(institutions.sheet) %>%
     select(institution:zip) %>%
     filter(!is.na(institution)) %>%
     mutate(merged_address = paste(address, city, state, zip, sep = " ")) %>%
     mutate_geocode(merged_address) %>%
     filter(!is.na(lon) & !is.na(lat))


```

```{r map_of_locations, include = TRUE}

leaflet() %>%
     addProviderTiles(providers$CartoDB.Positron) %>%
     addCircleMarkers(lng=institutions$lon,
                      lat=institutions$lat,
                      fillColor = mna.blue,
                      fillOpacity = .25,
                      popup = institutions$institution)
```







# Demographics of Training Participants

## Number of years of experience of participants

```{r years_of_experience}

experience <- pre.surveys %>%
     select(training_year, training_type, how_long_have_you_managed_the_budget_s_for_a_federal_trio_program_at_your_current_institution_whole_number_only) %>%
     set_names("training_year", "training_type", "years_experience") %>%
     mutate(years_experience = str_replace(years_experience, "90 days", "3 months")) %>%
     mutate(years_experience = str_replace(years_experience, ">1", "")) %>%
     mutate(years_experience = str_replace(years_experience, "3 weeks", "1 month")) %>%
     mutate(years_experience = str_replace(years_experience, "2015", "3 years")) %>%
     mutate(years_experience = str_replace(years_experience, "1yr", "1 year")) %>%
     mutate(years_experience = str_replace(years_experience, "90 days", "3 months")) %>%
     mutate(months_or_years = ifelse(str_detect(years_experience, "month"), "months", "years")) %>%
     mutate(years_calculated = parse_number(years_experience)) %>%
     mutate(years_calculated = ifelse(months_or_years == "years", years_calculated, years_calculated / 12)) %>%
     mutate(years_calculated = round(years_calculated, 1)) %>%
     group_by(training_year, training_type) %>%
     summarize(avg_years = round(mean(years_calculated, na.rm = TRUE), 1)) %>%
     arrange(training_year) 

dk_table(experience, c("Year", "Training", "Years of Experience"))


```



```{r attended_previous_training}
attended.previous <- pre.surveys %>%
     select(training_year, training_type, have_you_attended_a_similar_trio_training_program_in_the_past) %>%
     rename("attended_previous" = have_you_attended_a_similar_trio_training_program_in_the_past) %>%
     group_by(training_year, training_type) %>%
     count(attended_previous) %>%
     mutate(session = paste(training_type, 
                            " (",
                            training_year,
                            ")",
                            sep = "")) %>%
     mutate(pct = dk_proportions(n)) %>%
     mutate(popup_text = paste(attended_previous,
                               " (",
                               percent(pct),
                               ")",
                               sep =""))

```

```{r attended_previous_training_plot, include = TRUE, fig.height=3}

p <- ggplot(attended.previous, aes(x = session, 
                                   y = pct,
                                   text = popup_text,
                                   fill = attended_previous)) +
     geom_bar(stat = "identity", position = "stack") +
     coord_flip() +
     scale_y_continuous(labels = percent) +
     scale_fill_manual(values = c(mna.red, 
                                  mna.medium.gray, 
                                  mna.blue)) +
     mna.bar.chart.theme

ggplotly(p, tooltip = "popup_text")
```



## Currently, are you one of the main budget-related decision makers at your institution?  

```{r decision_makers}
decision.makers <- pre.surveys %>%
     filter(training_id == "2018 Online") %>%
     select(currently_are_you_one_of_the_main_budget_related_decision_makers_at_your_institution) %>%
     set_names("response") %>%
     group_by(response) %>%
     count() %>%
         mutate(popup_text = paste(response,
                               n,
                               sep = ": ")) 


```

```{r, include = TRUE, fig.height = 2}


p <- ggplot(decision.makers, aes(x = response,
                            y = n,
                            text = popup_text,
                            fill = factor(response))) +
     geom_bar(stat = "identity") +
     coord_flip() +
     scale_fill_manual(values = c(mna.red, mna.blue)) +
     mna.bar.chart.theme

ggplotly(p, tooltip = "popup_text")

```


### If no, how many other staff members work in your department?

```{r}
other.staff <- pre.surveys %>%
     filter(training_id == "2018 Online") %>%
     select(if_no_how_many_other_staff_members_work_in_your_department_numerical_value_only) %>%
     set_names("number") %>%
     # mutate(number = as.integer(number))
     group_by(number) %>%
     count() %>%
     filter(!is.na(number)) %>%
     ungroup() %>%
     mutate(number = as.character(number)) %>%
     mutate(number = str_replace_all(number, c("2" = "Two",
                                               "3" = "Three",
                                               "4" = "Four",
                                               "5" = "Five",
                                               "6" = "Six",
                                               "7" = "Seven",
                                               "8" = "Eight",
                                               "9" = "Nine",
                                               "10" = "Ten"))) %>%
     mutate(number = paste(number, " other staff members", sep = "")) %>%
     mutate(number = factor(number, levels = rev(c("Two other staff members", 
                                                   "Three other staff members",
                                                   "Four other staff members",
                                                   "Five other staff members",
                                                   "Six other staff members",
                                                   "Seven other staff members",
                                                   "Nine other staff members",
                                                   "Ten other staff members")))) %>%
     mutate(popup_text = paste("Number of schools with ",
                               str_to_lower(number),
                               ": ",
                               n,
                               sep = ""))
     


```

```{r, include = TRUE, fig.height=4}
p <- ggplot(other.staff, aes(x = number, 
                             y = n,
                             text = popup_text)) +
     geom_bar(stat = "identity", fill = mna.blue) +
     coord_flip() +
     mna.bar.chart.theme 

ggplotly(p, tooltip = "popup_text")
```







# Pre-Training

## Currently, how would you rate your levels of knowledge and understanding of the following aspects of the training you are about to receive

```{r, include = TRUE}
p <- ggplot(filter(knowledge.growth, training_id == "2018 Online"), aes(x = item,
                           y = avg_rating,
                           text = popup_text)) +
     geom_bar(stat = "identity", fill = mna.blue) +
     coord_flip() +
     scale_y_continuous(limits = c(0, 4)) +
     mna.bar.chart.theme 

ggplotly(p, tooltip = "popup_text")
```





## What are some of your main expectations from the training?

```{r, include = TRUE}

summarize_open_ended_pre("what_are_some_of_your_main_expectations_from_the_training")

```

## What are some of the challenges that your institution currently faces as related to budget management in a Federal TRIO program?

```{r, include = TRUE}
summarize_open_ended_pre("what_are_some_of_the_challenges_that_your_institution_currently_faces_as_related_to_budget_management_in_a_federal_trio_program")
```

## Additional questions/comments regarding the training you are about to receive.

```{r, include = TRUE}
summarize_open_ended_pre("additional_questions_comments_regarding_the_training_you_are_about_to_receive")
```




# Course Ratings


## How would you rate the quality of the following course, topic or content area?


```{r course_ratings}
course.ratings <- post.surveys %>%
     select(contains("how_would_you_rate_the_quality"), training_type, training_year, training_id) %>%
     gather(key = "course", value = "rating", -training_year, -training_type, -training_id) %>%
     mutate(rating = parse_number(rating)) %>%
     mutate(rating = as.integer(rating)) %>%
     mutate(course = str_replace(course, "how_would_you_rate_the_quality_of_the_following_course_topic_or_content_area_", "")) %>%
     mutate(course = str_replace_all(course, "_", " ")) %>%
     mutate(course = str_to_title(course)) %>%
     filter(rating != 0) %>%
     group_by(training_year, training_type, training_id, course) %>%
     summarize(avg_rating = round(mean(rating, na.rm = TRUE), 1)) %>%
     mutate(course = str_replace(course, "Ii", "II")) %>%
     mutate(course = str_wrap(course, width = 40)) %>%
     ungroup() %>%
     mutate(training_id = factor(training_id, levels = (c("2017 In person",
                                                         "2017 Hybrid",
                                                         "2017 Online",
                                                         "2018 Online")))) %>%
     mutate(popup_text = paste(course, 
                               "<br>",
                               training_type,
                               " (",
                               training_year,
                               ")<br>Average Rating: ",
                               as.character(avg_rating),
                               sep = ""))



```

```{r, include = TRUE, fig.height=8}

p <- ggplot(course.ratings, aes(x = training_id,
                           y = avg_rating,
                           text = popup_text,
                           fill = factor(training_id))) +
     geom_bar(stat = "identity", position = "dodge") +
     coord_flip() +
     scale_y_continuous(limits = c(0, 4)) +
     mna.bar.chart.theme +
     scale_fill_manual(guide = guide_legend(reverse = TRUE), 
                       values = rev(c(mna.blue, mna.green, mna.medium.gray, mna.red))) +
     facet_wrap(~course, ncol = 2)

ggplotly(p, tooltip = "popup_text")

```

## If you rated low or medium on any of the items above, please mention why.

```{r, include = TRUE}

summarize_open_ended("if_you_rated_low_or_medium_on_any_of_the_items_above_please_mention_why") 

```


```{r}
summarize_open_ended("if_you_rated_low_or_medium_on_any_of_the_items_above_please_mention_why")
```


## To what extent were your general expectations of the training met?

```{r expectations_met, include = TRUE}
summarize_open_ended("to_what_extent_were_your_general_expectations_of_the_training_met")

```

## Please mention three (3) main take aways from the overall training




```{r takeaways, include = TRUE}
summarize_open_ended("please_mention_three_3_main_take_aways_from_the_overall_training")

```



# Satisfaction with Aspects of the Training

## Please rate the following aspects of the overall training
```{r aspects}
aspects <- post.surveys %>%
     select(contains("please_rate_the_following_aspects_of_the_overall_training"), training_type, training_year, training_id) %>%
     gather(key = "course", value = "rating", -training_year, -training_type, -training_id) %>%
     mutate(rating = parse_number(rating)) %>%
     mutate(rating = as.integer(rating)) %>%
     mutate(course = str_replace(course, "please_rate_the_following_aspects_of_the_overall_training_", "")) %>%
     mutate(course = str_replace_all(course, "_", " ")) %>%
     mutate(course = str_to_title(course)) %>%
     mutate(course = str_replace(course, "Material S", "Material(s)")) %>%
     mutate(course = str_replace(course, "Resource S", "Resources(s)")) %>%
     filter(rating != 0) %>%
     group_by(training_year, training_type, training_id, course) %>%
     summarize(avg_rating = round(mean(rating, na.rm = TRUE), 1)) %>%
     mutate(course = str_replace(course, "Ii", "II")) %>%
     mutate(course = str_wrap(course, width = 40)) %>%
     mutate(popup_text = paste(course, 
                               "<br>",
                               training_type,
                               " (",
                               training_year,
                               ")<br>Average Rating: ",
                               as.character(avg_rating),
                               sep = ""))

```


```{r aspects_plot, fig.height = 10, include = TRUE}

p <- ggplot(aspects, aes(x = training_id,
                           y = avg_rating,
                           text = popup_text,
                           fill = factor(training_id))) +
     geom_bar(stat = "identity", position = "dodge") +
     coord_flip() +
     scale_y_continuous(limits = c(0, 4)) +
     mna.bar.chart.theme +
     scale_fill_manual(guide = guide_legend(reverse = TRUE), 
                       values = rev(c(mna.blue, mna.green, mna.medium.gray, mna.red))) +
     facet_wrap(~course, ncol = 2)

ggplotly(p, tooltip = "popup_text")
```

## If you rated low or medium, please mention why.

```{r, include = TRUE}
summarize_open_ended("if_you_rated_low_or_medium_please_mention_why")
```

## Live webinar


```{r}
live.webinar <- post.surveys %>%
     select(if_you_participated_in_the_live_webinar_how_helpful_was_it_to_have_an_opportunity_for_online_participants_to_connect_directly_with_a_speaker) %>%
     set_names("response") %>%
     filter(!is.na(response)) %>%
     filter(response != "I did not participate in the live webinar") %>%
     count(response) %>%
     mutate(popup_text = paste(response, n, sep = ": ")) %>%
     arrange(-n)
```
### If you participated in the live webinar, how helpful was it to have an opportunity for online participants to connect directly with a speaker?

```{r, include = TRUE, fig.height = 2}

# dk_table(live.webinar, c("Response", "Number"))

p <- ggplot(live.webinar, aes(x = response, 
                           y = n,
                           text = popup_text,
                           fill = response)) +
     geom_bar(stat = "identity", position = "stack") +
     coord_flip() +
     # scale_y_continuous(labels = percent) +
     scale_fill_manual(values = c(mna.red, 
                                  mna.green,
                                  mna.blue)) +
     mna.bar.chart.theme 

ggplotly(p, tooltip = "popup_text")

```

### Is there anything you would suggest that we do differently for the live webinar?
```{r, include = TRUE}
summarize_open_ended("is_there_anything_you_would_suggest_that_we_do_differently_for_the_live_webinar")
```




# Knowledge Growth


Below are the results for the <span style="color:#F05356; font-weight: 700;">pre</span> and <span style="color:#2BAADF; font-weight: 700;">post</span> self-assessments of participant knowledge in various areas. The larger the gap between the red and blue dots, the greater the knowledge growth that occured for participants.

```{r knowledge_growth_plot, include = TRUE, fig.height = 10}

p <- ggplot(knowledge.growth,
       aes(x = avg_rating, 
           y = training_id,
           group = training_id,
           text = popup_text,
           fill = factor(timing),
           color = factor(timing))) +
     geom_line() +
     geom_point() +
     facet_wrap(~item, ncol = 2) + 
     mna.bar.chart.theme +
     scale_fill_manual(values = c(mna.red, mna.blue)) +
     scale_color_manual(values = c(mna.red, mna.blue)) +
     scale_x_continuous(limits = c(0, 4))

ggplotly(p, tooltip = "popup_text")

```






# General Feedback

## Are there any additional topic(s) that could be added in future training(s)?

```{r, include=TRUE}
summarize_open_ended("are_there_any_additional_topic_s_that_could_be_added_in_future_training_s")
```

## Would you like a follow-up training session on the same topic(s)?

```{r}
follow.up <- post.surveys %>%
     filter(training_id == "2018 Online") %>%
     select(would_you_like_a_follow_up_training_session_on_the_same_topic_s) %>%
     set_names("response") %>%
     filter(!is.na(response)) %>%
     count(response) %>%
     mutate(pct = dk_proportions(n)) %>%
     mutate(response = factor(response, levels = c("Yes", "Maybe", "No"))) %>%
     mutate(popup_text = paste(response,
                               "<br>",
                               n,
                               " (",
                               percent(pct),
                               ")",
                               sep = ""))
```


```{r, include=TRUE, fig.height=3, fig.width=6}

p <- ggplot(follow.up, aes(x = response, 
                           y = n,
                           text = popup_text,
                           fill = response)) +
     geom_bar(stat = "identity", position = "stack") +
     coord_flip() +
     # scale_y_continuous(labels = percent) +
     scale_fill_manual(values = c(mna.blue, 
                                  mna.medium.gray, 
                                  mna.red)) +
     mna.bar.chart.theme 

ggplotly(p, tooltip = "popup_text")
```


## Will you recommend this training to your colleague(s)?

```{r}
recommend.training <- post.surveys %>%
     filter(training_id == "2018 Online") %>%
     select(will_you_recommend_this_training_to_your_colleague_s) %>%
     set_names("response") %>%
     filter(!is.na(response)) %>%
     count(response) %>%
     mutate(pct = dk_proportions(n)) %>%
     mutate(response = factor(response, levels = c("Yes", "Maybe", "No"))) %>%
     mutate(popup_text = paste(response,
                               "<br>",
                               n,
                               " (",
                               percent(pct),
                               ")",
                               sep = ""))
```

```{r, fig.height=3, fig.width=6, include=TRUE}

p <- ggplot(recommend.training, aes(x = response, 
                                    y = n,
                                    text = popup_text,
                                    fill = response)) +
     geom_bar(stat = "identity", position = "stack") +
     coord_flip() +
     # scale_y_continuous(labels = percent) +
     scale_fill_manual(values = c(mna.blue, 
                                  mna.medium.gray, 
                                  mna.red)) +
     mna.bar.chart.theme 

ggplotly(p, tooltip = "popup_text")
```



```{r bookdown, eval = FALSE}

gitbook(split_by = "none")
render_book("trio_survey_reports.Rmd", "bookdown::gitbook", output_dir = "docs")
```